### 2016-07-15 ch01-intro/introduction.tex
Two groups of users -> range of users

In this dissertation, we focus on developing system identification techniques that are `user-friendly'.
The availability of easy to use and fast methods has been underlined by \citet{Gevers2011Challenges}.
In this context, `user-friendly' should be understood as having a good user experience for two groups of users:
%TODO: more groups ("two groups")
\begin{itemize}
  \item novices, without formal training in system identification, optimization, \ldots and,
  \item well-seasoned identification practitioners that are already able to build good models.
\end{itemize}
Concretely, for novice users it is important to have straightforward techniques that require little interaction.
In practice, this boils down to methods that work well for a wide class of systems.
As such, only very generic assumptions of the system under test should be made and these should be easy to interpret.

>>>>

In this dissertation, we focus on developing system identification techniques that are `user-friendly'.
The availability of easy to use and fast methods has been underlined by \citet{Gevers2011Challenges}.
In this context, `user-friendly' should be understood as being easy to use for users ranging from novices to well-seasoned identification specialists.

Concretely, for novice users it is important to have straightforward techniques that require little interaction.
In practice, this boils down to methods that work well for a wide class of systems.
As such, only very generic assumptions of the system under test should be made and these should be easy to interpret.
